Data Exploration quad maps: IUCN and AquaMaps

### 2016-03-27 data_explore/data_explore_am_thresh.Rmd
updating boxplot figs and am threshold figs

hist_area_vs_threshold <- ggplot(spp_df3, aes(prop, fill = iucn_code)) + 
  ggtheme_plot + 
  geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 0.05, alpha = .7) + 
  geom_vline(xintercept = spp_df3_mean, color = 'darkred', linetype = 'dashed') + 
  annotate('text', x = spp_df3_mean, y = .13, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'mean') + 
  geom_vline(xintercept = spp_df3_med, color = 'grey30', linetype = 'dashed') + 
  annotate('text', x = spp_df3_med, y = .13, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'median') + 
  scale_fill_manual(values = c('LC' = 'green4', 
                               'NT' = 'greenyellow', 
                               'VU' = 'orange', 
                               'EN' = 'orangered2', 
                               'CR' = 'red4',
                               'EX' = 'black',
                               'DD' = 'grey60',
                               'NE' = 'grey70')) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1.02)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = 'Proportion of range included when selecting a threshold of 40%', 
       y = sprintf('Proportion of all aquamaps species (n = %s)', nrow(spp)),
       fill = 'IUCN code')

@@

ggsave(file.path(dir_fig, 'si_am_threshold.tif'), device = 'tiff', 
       width = 17.8, height = 9, units = 'cm')
ggsave(file.path(dir_fig, 'si_am_threshold.png'), 
       width = 17.8, height = 9, units = 'cm')

@@

  geom_ribbon(aes(ymax = quant95, ymin = quant05), alpha = .5, color = NA, fill = '#b8e186') +
  geom_ribbon(aes(ymax = quant75, ymin = quant25), alpha = .5, color = NA, fill = '#4dac26') +
  geom_line(color = 'grey30') + 
  # geom_line(aes(y = mean_prop), color = 'darkgreen') + 
  # geom_abline(intercept = area_mean_model[['coefficients']][1],
  #             slope     = area_mean_model[['coefficients']][2],
  #             color = 'red') + 
  geom_vline(xintercept = 0.40, color = 'blue', linetype = 'dashed') +
  geom_vline(xintercept = 0.50, color = 'blue', linetype = 'dashed') +
  geom_vline(xintercept = 0.60, color = 'blue', linetype = 'dashed') +
  annotate('text', x = .39, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Halpern et al. 2012') + 
  annotate('text', x = .49, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Klein et al. 2015') + 
  annotate('text', x = .59, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'Kaschner et al. 2006') + 
  # annotate('text', x = .75, y = .85,
  #          #size = 3, 
  #          color = 'grey20',
  #          label = 'R^2^ = .995') + 
  scale_x_continuous(expand = c(0, 0), 
                     breaks = c(  .2,    .4,    .5,    .6,    .8,   1.0),
                     labels = c('20%', '40%', '50%', '60%', '80%', '100%'),
                     limits = c(0, 1.02)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 1.01)) +
  labs(# title = 'Relative species range after presence threshold',
       x = 'AquaMaps presence threshold cutoff', 
       y = 'Relative species range')

ggsave(file.path(dir_fig, 'si_ribbon_am_threshold.tif'), device = 'tiff', 
       width = 17.8, height = 7, units = 'cm')
ggsave(file.path(dir_fig, 'si_ribbon_am_threshold.png'), 
       width = 17.8, height = 7, units = 'cm')

>>>>

hist_area_vs_threshold <- ggplot(spp_df3, aes(prop, fill = iucn_code)) + 
  ggtheme_plot + 
  geom_histogram(aes(y = ..count../sum(..count..)), binwidth = 0.05, alpha = .7) + 
  geom_vline(xintercept = spp_df3_mean, color = 'darkred', linetype = 'dashed') + 
  annotate('text', x = spp_df3_mean, y = .13, hjust = 0, vjust = -.5,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'mean') + 
  geom_vline(xintercept = spp_df3_med, color = 'grey30', linetype = 'dashed') + 
  annotate('text', x = spp_df3_med + .02, y = .13, hjust = 0, vjust = 1,
           angle = 90, 
           size = 3, 
           color = 'grey20',
           label = 'median') + 
  scale_fill_manual(values = c('LC' = 'green4', 
                               'NT' = 'greenyellow', 
                               'VU' = 'orange', 
                               'EN' = 'orangered2', 
                               'CR' = 'red4',
                               'EX' = 'black',
                               'DD' = 'grey60',
                               'NE' = 'grey70')) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1.02)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = 'Proportion of range included for presence threshold = 40%', 
       y = sprintf('Proportion of all \nAquaMaps species (n = %s)', nrow(spp)),
       fill = 'IUCN code')

@@

ggsave(file.path(dir_fig, 'si_am_threshold.tif'), device = 'tiff', 
       width = 11.4, height = 6, units = 'cm')
ggsave(file.path(dir_fig, 'si_am_threshold.png'), 
       width = 11.4, height = 6, units = 'cm')

@@

  geom_ribbon(aes(ymax = quant95, ymin = quant05), alpha = .5, color = NA, fill = '#b8e186') +
  geom_ribbon(aes(ymax = quant75, ymin = quant25), alpha = .5, color = NA, fill = '#4dac26') +
  geom_line(color = 'grey30') + 
  # geom_line(aes(y = mean_prop), color = 'darkgreen') + 
  # geom_abline(intercept = area_mean_model[['coefficients']][1],
  #             slope     = area_mean_model[['coefficients']][2],
  #             color = 'red') + 
  geom_vline(xintercept = 0.40, color = 'blue', linetype = 'dashed') +
  geom_vline(xintercept = 0.50, color = 'blue', linetype = 'dashed') +
  geom_vline(xintercept = 0.60, color = 'blue', linetype = 'dashed') +
  annotate('text', x = .39, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 2, 
           color = 'grey20',
           label = 'Halpern et al. 2012') + 
  annotate('text', x = .49, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 2, 
           color = 'grey20',
           label = 'Klein et al. 2015') + 
  annotate('text', x = .59, y = .03, hjust = 0, vjust = 0,
           angle = 90, 
           size = 2, 
           color = 'grey20',
           label = 'Kaschner et al. 2006') + 
  # annotate('text', x = .75, y = .85,
  #          #size = 3, 
  #          color = 'grey20',
  #          label = 'R^2^ = .995') + 
  scale_x_continuous(expand = c(0, 0), 
                     breaks = c(  .2,    .4,    .5,    .6,    .8,   1.0),
                     labels = c('20%', '40%', '50%', '60%', '80%', '100%'),
                     limits = c(0, 1.02)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 1.01)) +
  labs(# title = 'Relative species range after presence threshold',
       x = 'AquaMaps presence threshold cutoff', 
       y = 'Relative species range')

ggsave(file.path(dir_fig, 'si_ribbon_am_threshold.tif'), device = 'tiff', 
       width = 11.4, height = 6, units = 'cm')
ggsave(file.path(dir_fig, 'si_ribbon_am_threshold.png'), 
       width = 11.4, height = 6, units = 'cm')
